Supplementary Information: Optimizing Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD Transient

### 2019-10-20 paper/cvpr2020/main.tex
pass over paper

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
abstract
\end{abstract}

>>>>

\def\cvprPaperID{2224} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Existing monocular depth estimation algorithms successfully predict the relative depth {order} of objects in a scene.
However, because of the fundamental scale ambiguity associated with monocular images, these algorithms fail at correctly predicting an object's true metric depth. 
In this work, we demonstrate how a depth histogram of the scene, which can be readily captured using a single-pixel diffused single-photon avalanche diode (SPAD), can be fused with the output of existing monocular depth estimation algorithms to resolve the depth ambiguity problem. 
We validate this novel sensor fusion technique experimentally and in extensive simulation. We show that it dramatically improves the performance of several state-of-the-art monocular depth estimation algorithms.
\end{abstract}

### 2019-10-20 paper/cvpr2020/sections/discussion.tex
pass over paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Future Work}
While our hardware prototype is very large, future work could be done to
miniaturize this system. Our algorithm or similar sensor fusion algorithms could
also be integrated into electronics that already contain the required hardware
components, for example, existing cell phones with single-pixel SPAD
proximity sensors and RGB cameras.

Other methods for extracting scene information from the SPAD histogram could be
also employed, including learning-based methods to combine the MDE and
histogram. One might even consider sensing regimes where the number of
returning signal photons is very low, such as when the SPAD and camera operate
at high framerates. While most MDE techniques are tailored to clean RGB images,  
the SPAD histogram could potentially be used to help MDE
techniques generalize to noisy scenes under low-light conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}
Since their introduction, the performance of monocular depth estimation algorithms has improved tremendously.  However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements. 
This suggests we are approaching the limits of what can be achieved using a monocular image alone. 
In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histograms measurements. 
Such histograms are cheap to capture using SPADs and are poised to become an important component of future low-cost imaging systems.
%Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.
%Computational photography approaches may provide the measurements needed to achieve much greater performance improvements, especially as the sensors in devices we use every day become more diverse, complex, and increasingly rely on techniques based on sensor fusion and sophisticated computational algorithms.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Future Work}
While our hardware prototype is large, future work could miniaturize this system. Our algorithm or similar sensor fusion algorithms could
also be integrated into electronics that already contain the required hardware
components, for example, existing cell phones with single-pixel SPAD
proximity sensors and RGB cameras.

Other methods for extracting scene information from the SPAD histogram could be
also employed, including learning-based methods to combine the MDE and
histogram. One might even consider sensing regimes where the number of
returning signal photons is low, such as when the SPAD and camera operate
at high framerates. While most MDE techniques are tailored to clean RGB images,  
the SPAD histogram could be used to help MDE
techniques generalize to noisy scenes under low-light conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}
Since their introduction, the performance of monocular depth estimation algorithms has improved tremendously.  However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements. 
This suggests we are approaching the limits of what can be achieved using a monocular image alone. 
In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histograms measurements. 
Such histograms are easy to capture using SPADs and are poised to become an important component of future low-cost imaging systems.
%Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.
%Computational photography approaches may provide the measurements needed to achieve much greater performance improvements, especially as the sensors in devices we use every day become more diverse, complex, and increasingly rely on techniques based on sensor fusion and sophisticated computational algorithms.

### 2019-10-20 paper/cvpr2020/sections/hardware.tex
pass over paper

The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps. The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth map with an accuracy of about 1~cm. A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene. This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth. The monocular depth estimate is calculated using the RGB image captured by the Kinect v2.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured.pdf}
	\caption{Experimental results. For each scene, we record a ground truth depth map that is raster-scanned with the SPAD (upper left subimages), and an RGB image (lower left subimages). A monocular depth CNN predicts an initial depth map (top middle subimages), which is corrected with the diffused SPAD histogram using the proposed method (top right subimages). As shown by the error maps and root mean squared error (RMSE) for each example (lower center, right subimages). The CNN is confused when we show it a photograph of a poster (bottom scene); it incorrectly predicts the depth of the scene depicted on the flat print. Our method is able to correct this error. }
	\label{fig:results_captured}
\end{figure}

>>>>

The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps. The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth maps with an accuracy of about 1~cm. A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene. This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth. The monocular depth estimate is calculated using the RGB image captured by the Kinect v2.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured.pdf}
	\caption{Experimental results. For each scene, we record a ground truth depth map that is raster-scanned with the SPAD (upper left subimages), and an RGB image (lower left). A monocular depth CNN predicts an initial depth map (top middle), which is corrected with the diffused SPAD histogram using the proposed method (top right). As shown by the error maps and root mean squared error (RMSE) for each example (lower center, right). The CNN is confused when we show it a photograph of a poster (bottom scene); it incorrectly predicts the depth of the scene depicted on the flat print. Our method is able to correct this error. }
	\label{fig:results_captured}
\end{figure}

### 2019-10-20 paper/cvpr2020/sections/introduction.tex
pass over paper

Here, we propose to use a single-pixel SPAD and pulsed light source in an unconventional way: rather than optically focusing them to record the distance to a single scene point, we diffuse the emitted light and the detector over the entire scene. The resulting measurement resembles a histogram of the depth of the scene and can be used to achieve accurate absolute depth when combined with a monocular depth estimate (\cf~Figure~\ref{fig:teaser}).

@@

To this end, we develop a sensor fusion strategy that processes the ordinal depth computed by a monocular depth estimator to be consistent with the measurements captured by the diffused SPAD. We demonstrate in extensive simulations that our approach achieves substantial improvements in the quality of the estimated depth maps, regardless of which specific depth estimator is used. Moreover, we build an RGB-SPAD camera prototype and demonstrate in practice that our sensor fusion strategy achieves significantly higher-quality depth maps for a variety of captured scenes compared to MDE alone. With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware. Specifically, we make the following contributions:
%
\begin{itemize}
	\item We propose augmenting an RGB camera with a global depth histogram captured by a SPAD to address scale ambiguity error in monocular depth estimators.	
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
	\item We build a prototype RGB-SPAD camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types. 
\end{itemize}

>>>>

Here, we propose to use a single-pixel SPAD and pulsed light source in an unconventional way: rather than optically focusing them to record the distance to a single scene point, we diffuse the emitted light and the detector over the entire scene. The resulting measurement resembles a histogram of the depth of the scene and we demonstrate that this can be used to achieve accurate absolute depth when combined with a monocular depth estimate (\cf~Figure~\ref{fig:teaser}).

@@

To this end, we develop a sensor fusion strategy that processes the ordinal depth computed by a monocular depth estimator to be consistent with the measurements captured by the diffused SPAD. We demonstrate in extensive simulations that our approach achieves substantial improvements in the quality of the estimated depth maps, regardless of which specific depth estimator is used. Moreover, we build an RGB-SPAD camera prototype and demonstrate in practice that our sensor fusion strategy achieves significantly higher-quality depth maps for a variety of captured scenes compared to MDE alone. With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware. Specifically, we make the following contributions:
%
\begin{itemize}
	\item We propose augmenting an RGB camera with a global depth histogram captured by a diffused SPAD to address scale ambiguity error in monocular depth estimators.	
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
	\item We build a prototype RGB-SPAD camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types. 
\end{itemize}

### 2019-10-20 paper/cvpr2020/sections/method.tex
pass over paper

In this section, we describe the image formation of a diffused pulsed laser and single-photon avalanche diode (SPAD). We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the diffused SPAD.

@@

Consider a diffused laser that emits a pulse at time $t = 0$ with time-varying
intensity $g(t)$ illuminating some 3D scene. We parameterize the geometry of the
scene as a distance map $z(x, y)$, where each of the 3D points has also some
unknown reflectivity $\alpha$ at the wavelength of the laser. Ignoring
interreflections of the emitted light within the scene, a single-pixel diffused
SPAD integrates light scattered back from the scene onto the detector as
%
\begin{equation}
	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \frac{\alpha \left( x,y \right)}{z(x,y)^2} \cdot  g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
	\label{eq:pulse_integral} 
\end{equation}  
%
where $c$ is the speed of light, $\Omega_{x,y}$ is the spatial extent of the
diffused light, and we assume that the light is diffused uniformly over the
scene points. Each time such a light pulse is emitted into the scene and
scattered back to the detector, the single-pixel SPAD time-stamps up to one of
the returning photons with some probability. The process is repeated millions of
times per second with the specific number of emitted pulses being controlled by
the repetition rate of the laser.  Each detected photon arrival event is
discretized into a histogram $h$ of the form
%
\begin{equation}
  h[n] \sim \mathcal{P} \left( \eta \int_{n\Delta t}^{(n+1)\Delta t} \left(f * s \right) \left( t \right)  dt + b \right),	
	\label{eq:spad_measurements}
\end{equation}
%
where $(n\Delta t, (n+1) \Delta t)$ models the $n^\text{th}$ time interval or bin of the
temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$
is a function that models the temporal uncertainty in the detector, and $b$
represents background detections from ambient light and false positive detections known as \textit{dark
count}. As derived in previous work, the combination of signal and background
can be modeled as an inhomogeneous Poisson process
$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, we adopt the term
\textit{transient} for the histogram $h[n]$~\cite{Xin2019}.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{method.pdf}
  \caption{Overview of processing pipeline. The processing pipeline uses
      the input SPAD measurements and an RGB image to produce an accurate depth
      map. The SPAD measurements are pre-processed to adjust for ambient photon
      detections, radiometric falloff factors, and to calibrate the bin widths.
      From the RGB image, an MDE estimates an initial depth map
      and the scene reflectance is estimated. A reflectance-weighted
      depth histogram is compared to the processed SPAD measurements to
      calculate a histogram matching matrix which is used to output the corrected depth map.
  }
  \label{fig:pipeline}
\end{figure}

@@

\vspace{0.8em}\noindent{\bf Background Subtraction.}
In the first step, we remove the background counts from the
transient by initally estimating the average amount of background counts
in each time bin. For nearly all natural scenes, the closest objects to the
camera are a finite distance away, and so the first bins of the SPAD
measurement contain only background counts without any backscattered
signal. We can therefore estimate the
average number of background and noise counts $\hat{b}$ as 
%
\begin{equation}
  \hat b = \frac{1}{N}\sum_{n=0}^N h[n]. 
  \label{eq:ambient_estimate}
\end{equation}
%
where we choose the number of bins $N$ to correspond to time
values before the backscattered signal arrives.

@@

\vspace{0.8em}\noindent{\bf Falloff Compensation.}
In the second step, we compensate for distance falloff effects by multiplying the histogram
by distance-dependent scaling factor,
\begin{equation}
    h'[n] = h[n] \cdot r_n^2.
  \label{eq:h_scaled}
\end{equation}
Here, $r_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
corresponding to bin $n$, and this radiometric falloff model is consistent with
measurements captured with our hardware prototype.

@@

Finally, we use the movement matrix $T$ to shift the pixels of the MDE depth map
to match the global depth of the target histogram. For a depth map pixel with
depth bin $k$, we select the corrected bin by sampling from the distribution $T[k,
:]/\sum_{n=1}^NT[k,n]$. This sampling procedure handles the
case where a single input depth bin of the MDE is mapped to
multiple output bins~\cite{Morovic2002}.
%
\begin{algorithm}[H]
 \caption{Find Pixel Movement} 
 \label{alg:ehm}
 \begin{algorithmic}
  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
    \State Initialize $T$ as an $M \times N$ array of zeros.
    \For{$m$ in $1,\ldots,M$}
      \For{$n$ in $1,\ldots,N$}
        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
      \EndFor
    \EndFor
    \State \textbf{return} $T$
  \EndProcedure
 \end{algorithmic}
\end{algorithm}
%

>>>>

In this section, we describe the image formation of a diffused pulsed laser and single-photon avalanche diode (SPAD). We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the SPAD.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{method.pdf}
  \caption{Overview of processing pipeline. The processing pipeline uses
      the input SPAD measurements and an RGB image to produce an accurate depth
      map. The SPAD measurements are pre-processed to adjust for ambient photon
      detections, radiometric falloff factors, and to calibrate the bin widths.
      From the RGB image, an MDE estimates an initial depth map
      and the scene reflectance is estimated. A reflectance-weighted
      depth histogram is compared to the processed SPAD measurements to
      calculate a histogram matching matrix which is used to output the corrected depth.
  }
  \label{fig:pipeline}
\end{figure}

Consider a diffused laser that emits a pulse at time $t = 0$ with time-varying
intensity $g(t)$ illuminating some 3D scene. We parameterize the geometry of the
scene as a distance map $z(x, y)$, where each of the 3D points has also some
unknown reflectivity $\alpha$ at the wavelength of the laser. Ignoring
interreflections of the emitted light within the scene, a single-pixel diffused
SPAD integrates light scattered back from the scene onto the detector as
%
\begin{equation}
	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \frac{\alpha \left( x,y \right)}{z(x,y)^2} \cdot  g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
	\label{eq:pulse_integral} 
\end{equation}  
%
where $c$ is the speed of light, $\Omega_{x,y}$ is the spatial extent of the
diffused light, and we assume that the light is diffused uniformly over the
scene points. Each time such a light pulse is emitted into the scene and
scattered back to the detector, the single-pixel SPAD time-stamps up to one of
the returning photons with some probability. The process is repeated millions of
times per second with the specific number of emitted pulses being controlled by
the repetition rate of the laser.  Each detected photon arrival event is
discretized into a histogram $h$ of the form
%
\begin{equation}
  h[n] \sim \mathcal{P} \left( \eta \int_{n\Delta t}^{(n+1)\Delta t} \left(f * s \right) \left( t \right)  dt + b \right),	
	\label{eq:spad_measurements}
\end{equation}
%
where $[n\Delta t, (n+1) \Delta t)$ models the $n^\text{th}$ time interval or bin of the
temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$
is a function that models the temporal uncertainty in the detector, and $b$
represents background detections from ambient light and false positive detections known as \textit{dark
count}. As derived in previous work, the combination of signal and background
can be modeled as an inhomogeneous Poisson process
$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, we adopt the term
\textit{transient} for the histogram $h[n]$~\cite{Xin2019}.

@@

\vspace{0.8em}\noindent{\bf Background Subtraction.}
In the first step, we remove the background counts from the
transient by initially estimating the average amount of background counts
in each time bin. For nearly all natural scenes, the closest objects to the
camera are a finite distance away, and so the first bins of the SPAD
measurement contain only background counts without any backscattered
signal. We can therefore estimate the
average number of background and noise counts $\hat{b}$ as 
%
\begin{equation}
  \hat b = \frac{1}{N}\sum_{n=0}^N h[n]. 
  \label{eq:ambient_estimate}
\end{equation}
%
where we choose the number of bins $N$ to correspond to time
values before the backscattered signal arrives.

@@

\vspace{0.8em}\noindent{\bf Falloff Compensation.}
In the second step, we compensate for distance falloff effects by multiplying the histogram
by distance-dependent scaling factor,
\begin{equation}
    h'[n] = h[n] \cdot z_n^2.
  \label{eq:h_scaled}
\end{equation}
Here, $z_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
corresponding to bin $n$, and this radiometric falloff model is consistent with
measurements captured with our hardware prototype.

@@

Finally, we use the movement matrix $T$ to shift the pixels of the MDE depth map
to match the global depth of the target histogram. For a depth map pixel with
depth bin $k$, we select the corrected bin by sampling from the distribution $T[k,
:]/\sum_{n=1}^NT[k,n]$. This sampling procedure handles the
case where a single input depth bin of the MDE is mapped to
multiple output bins~\cite{Morovic2002}.
%

{ \footnotesize
\begin{algorithm}[H]
 \caption{Find Pixel Movement} 
 \label{alg:ehm}
 \begin{algorithmic}
	\footnotesize
  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
    \State Initialize $T$ as an $M \times N$ array of zeros.
    \For{$m$ in $1,\ldots,M$}
      \For{$n$ in $1,\ldots,N$}
        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
      \EndFor
    \EndFor
    \State \textbf{return} $T$
  \EndProcedure
 \end{algorithmic}
\end{algorithm}
}
%

### 2019-10-20 paper/cvpr2020/sections/related.tex
pass over paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}
%
Estimating a depth map from a single RGB image has been approached using Markov Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural networks have been applied to this problem. For example, Eigen et al.~\cite{Eigen2014} use a multi-scale neural network to
predict depth maps, Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a network using stereo pairs, and Fu et al.~\cite{Fu2018} combine a logarithmic depth discretization scheme with an ordinal regression loss function. Various experiments using different types of encoder networks (e.g. ResNet, DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some success, as have approaches mixing deep learning with conditional random fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}. Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of monocular depth estimation using cross-dataset transfer.

@@

In our procedure, the diffused SPAD measurements capture a histogram of the depth map where the histogram values are weighted by spatially varying scene reflectances and inverse-square falloff effects. We therefore adapt the algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general per-pixel weights during histogram matching.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}
%
Estimating a depth map from a single RGB image has been approached using Markov Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural networks have been applied to this problem. For example, Eigen et al.~\cite{Eigen2014} use a multi-scale neural network to
predict depth maps, Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a network using stereo pairs, and Fu et al.~\cite{Fu2018} combine a logarithmic depth discretization scheme with an ordinal regression loss function. Various experiments using different types of encoder networks (\eg ResNet, DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some success, as have approaches mixing deep learning with conditional random fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}. Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of monocular depth estimation using cross-dataset transfer.

@@

In our procedure, the diffused SPAD measurements closely resemble a histogram of the depth map where the histogram values are weighted by spatially varying scene reflectances and inverse-square falloff effects. We therefore adapt the algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general per-pixel weights during histogram matching.

### 2019-10-20 paper/cvpr2020/sections/simulation.tex
pass over paper

To simulate a SPAD histogram, we take the provided depth map and 
calculate a weighted depth histogram by weighting the pixel contributions to
each depth bin by the luminance of each pixel. To model radiometric falloff, we
multiply each bin by $1/z^2$, and convolve with a modeled system temporal
response, which we approximate as a Gaussian with a full-width at half-maximum of 70ps. We scale
the histogram by the total number of observed signal photon counts (set to 
$10^6$) and  add a fixed number of background photons $b \in \set{10^5, 2\times
10^4, 10^4}$. The background counts are evenly distributed across all bins to simulate the ambient and dark
count detections, and the different background levels correspond to
signal-to-background ratios (SBR) of $10, 50$ and $100$ respectively. Finally,
each bin is Poisson sampled to produce the final simulated SPAD transient.

>>>>

To simulate a SPAD histogram, we take the provided depth map and 
calculate a weighted depth histogram by weighting the pixel contributions to
each depth bin by the luminance of each pixel. To model radiometric falloff, we
multiply each bin by $1/z^2$, and convolve with a modeled system temporal
response, which we approximate as a Gaussian with a full-width at half-maximum of 70~ps. We scale
the histogram by the total number of observed signal photon counts (set to 
$10^6$) and  add a fixed number of background photons $b \in \set{10^5, 2\times
10^4, 10^4}$. The background counts are evenly distributed across all bins to simulate the ambient and dark
count detections, and the different background levels correspond to
signal-to-background ratios (SBR) of $10, 50$ and $100$ respectively. Finally,
each bin is Poisson sampled to produce the final simulated SPAD transient.
